---
title: "9_CISI_actual"
author: "tsuyoshi"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_folding: "hide"
    pandoc_args: [ 
      "--output=9_CISI_actual.html" 
    ]
date: "`r format(Sys.time(), '%d %B, %Y')`"

---

### setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(readr)
library(tidyr)
library(dplyr)
library(tibble)
library(ComplexHeatmap)
library(RColorBrewer)
library(ggsci)
```


### input data
```{r specify_paths_1}

project.path <- "/mnt/projects/data/publication_2/9_CISI_actual"
# Specify input paths
genewise.path <- file.path(project.path,"result_genewise.csv")
cisich.path <- file.path(project.path,"result_cisich_corr.csv")
summary.path <- file.path(project.path,"result_summary.csv")
```

```{r}
df_summary <- read.csv(summary.path,  row.names = 'X') 
df_genewise <- read_csv(genewise.path,show_col_types = F) 
df_cisich <- read.csv(cisich.path,  row.names = 'X')
```


```{r reshape_df}
# pivot longer for ggplot
df_summary$Condition <- rownames(df_summary)
df_summary <-df_summary %>% 
  pivot_longer(c('Gene_average','Gene_minimum','Cell_average'), 
               names_to = "value_type", values_to = "Correlation")

df_genewise <- df_genewise %>% 
  `colnames<-`(sub("...1","Condition",colnames(.), fixed = T) ) %>%
  pivot_longer(!Condition, names_to = "Marker", values_to = "Correlation")

df_cisich$cisi_channel <- rownames(df_cisich)
df_cisich <- df_cisich %>%
  pivot_longer(!cisi_channel, names_to = "Condition", values_to = "Correlation")
```

### plot summary
```{r, results="asis",fig.height = 3, fig.width =8, fig.align = "center"}
ggplot(df_summary, 
       aes(x = Condition, y = Correlation, fill = Condition)) + 
  facet_wrap(~value_type) +
  geom_bar(stat = "identity") + theme_bw() + xlab(NULL) + 
  scale_y_continuous(expand = c(0,0),limits = c(0,1)) +
  scale_fill_npg() +
  # geom_text(aes(label = sprintf("%.3f",Correlation)), vjust = -0.3) +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.border = element_blank(), 
        strip.background = element_blank(),
        strip.text = element_text(face = "bold", size = 12),
        axis.line = element_line())
```

### plot all conditions for all proteins
```{r, results="asis",fig.height = 3, fig.width =8, fig.align = "center"}
ggplot(df_genewise, 
       aes(x = reorder(Marker, Correlation), y = Correlation, fill = Condition, group = Condition)) +
  geom_col(position =  position_dodge2(padding = 0.2),width = 0.7 ) + theme_bw() +
  xlab("Marker") + scale_y_continuous(expand = c(0,0),limits = c(0,1)) + scale_fill_npg() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        panel.border = element_blank(), 
        axis.line = element_line())
```

### plot Actual for all proteins
```{r, results="asis",fig.height = 3, fig.width =6, fig.align = "center"}
ggplot(df_genewise[df_genewise$Condition == "Actual",], 
       aes(x = reorder(Marker, Correlation), y = Correlation)) +
  geom_col(width = 0.7 , fill = "grey35") + theme_bw() +
  xlab("Marker") + scale_y_continuous(expand = c(0,0),limits = c(0,1)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),panel.border = element_blank(), axis.line = element_line()) 
```


### read A
```{r}
# read A
A_path <- "/mnt/projects/data/publication/9_CISI_actual/A.csv"
A <- read_csv(A_path,show_col_types = F) %>% column_to_rownames("...1")
A[A > 0] <- "labeled"
A[A == 0] <- "unlabeled"
```

### plot A and Ahat
```{r, results="asis",fig.height = 5, fig.width = 3, fig.align = "center"}

h1 <- Heatmap(t(A),
              col = c("unlabeled" = "white", "labeled" = "darkorange"),
              show_heatmap_legend = F, 
              cluster_columns = F, cluster_rows = F, # column_title = 'Correlation of \nactual_vs_simulated Y', 
              border = TRUE,rect_gp = gpar(col = "gray90", lwd = 1),
              top_annotation = columnAnnotation(
                corr = anno_barplot(df_cisich[df_cisich$Condition=='actual_vs_simulated_A',]$Correlation),
                height = unit(3, "cm"),show_annotation_name = FALSE))

h1

```

## single-cell analyses

### load additional libraries
```{r}
library(SingleCellExperiment)
library(zellkonverter)
library(doParallel)
library(scater)
library(uwot)
library(caret)
library(ROSE)
library(colorRamp2)
library(pROC)
```


### set input
```{r specify_paths_2}
# Specify input paths
sce_gt.path <- file.path(project.path,"sce/sce_gt.h5ad")
sce_dc.path <- file.path(project.path,"sce/sce_dc_Actual.h5ad")

```

### input sces
```{r}
# read h5ad to sce
sce_gt <- readH5AD(sce_gt.path) 
sce_dc <- readH5AD(sce_dc.path)

# combine sces into list
SCE <- list(sce_gt,sce_dc)
names(SCE) <- c("ground_truth", "decompressed" )
```



### add arcsinh transformed and scaled counts
```{r add_exprs_scaled}
# set function for scaling
scale_sce <- function(sce, assay = "exprs", percent = 0.9999){
  # assay(sce, "exprs") <- asinh(assay(sce, "counts") / 2)
  es <- assay(sce, assay)
  qs <- rowQuantiles(es, probs = c(0.0, percent))
  x <- (es - qs[, 1]) / (qs[, 2] - qs[, 1])
  x[x < 0] <- 0; x[x > 1] <- 1
  return(x)
}

SCE <- lapply(SCE, function(sce) {
              assay(sce, "exprs") <- asinh(counts(sce)/1)
              assay(sce, "scaled") <- scale_sce(sce)
              sce
            })

```


### run UMAP
```{r runUMAP}
SCE <- lapply(SCE, function(sce){
  set.seed(240508)
  sce <- runUMAP(sce, exprs_values="exprs", n_threads = 20)
  sce
})
```

### train Random forest classfier using ground truth data
```{r}
sce <- SCE$ground_truth
```

#### make labels for training based on threshold of scaled expression
```{r}
label_df <- 
  data.frame(Neut = as.numeric(assay(sce["MPO",],"scaled") > 0.3), 
             Fibro = as.numeric(assay(sce["SMA",],"scaled") > 0.7), 
             Endo = as.numeric(assay(sce["CD31",],"scaled") > 0.5), 
             Plasma = as.numeric(assay(sce["CD38",],"scaled") > 0.5), 
             NK = as.numeric(assay(sce["CD7",],"scaled") > 0.6 & 
                             assay(sce["CD3",],"scaled") < 0.2 & 
                             assay(sce["CD4",],"scaled") < 0.2 & 
                             assay(sce["CD8a",],"scaled") < 0.2), 
             migDC = as.numeric(assay(sce["DC-LAMP",],"scaled") > 0.5), 
             pDC = as.numeric(assay(sce["CD303",],"scaled") > 0.7), 
             Macro1 = as.numeric(assay(sce["CD68",],"scaled") > 0.6 ),
             Macro2 = as.numeric(assay(sce["CD163",],"scaled") > 0.5), 
             B = as.numeric(assay(sce["CD20",],"scaled") > 0.4),
             Tc = as.numeric(assay(sce["CD8a",],"scaled") > 0.4 & 
                             assay(sce["CD4",],"scaled") < 0.4), 
             Treg = as.numeric(assay(sce["FOXP3",],"scaled") > 0.6 & 
                               assay(sce["CD3",],"scaled") > 0.1), 
             Th = as.numeric(assay(sce["CD4",],"scaled") > 0.5 & 
                             assay(sce["CD3",],"scaled") > 0.1 & 
                             assay(sce["FOXP3",],"scaled") < 0.5 & 
                             assay(sce["CD8a",],"scaled") < 0.3))
```

#### make final labels by selecting one cell type for the cells with multiple labels
```{r}
# define markers that define celltypes
celltypes <- c("Neut","Fibro","Endo" ,"Plasma","NK","migDC","pDC","Macro1","Macro2","B","Tc","Treg","Th")
markers <- c("MPO","SMA","CD31","CD38","CD7","DC-LAMP","CD303","CD68","CD163","CD20","CD4","FOXP3","CD8a")

# get celltype based on max marker expression (only used when multiple labels were assigned to a cell)
label_mat <- label_df %>% as.matrix() %>% t() # convert to matrix
max_celltype <- 
  (assay(sce[markers,],"scaled") * label_mat) %>% apply(2, which.max) %>% celltypes[.] 

# get final labeled cells by selecting "max_celltype" when multiple labels were assigned
RF_manual_label <- 
  ifelse(rowSums(label_df) > 1, max_celltype, 
    ifelse(rowSums(label_df) == 1, colnames(label_df)[apply(label_df, 1, which.max)],"unlabeled")) 

sce$RF_manual_label <- RF_manual_label

```

#### train RF with ROSE sampling for balancing the dataset
```{r}
# for parallel processing
ncore <- 15
cl <- makePSOCKcluster(ncore)
registerDoParallel(cl)

# Split between labeled and unlabeled cells
lab_spe <- sce[,sce$RF_manual_label != "unlabeled"]
unlab_spe <- sce[,sce$RF_manual_label == "unlabeled"]


# Randomly split into train and test data
set.seed(4)
trainIndex <- createDataPartition(factor(lab_spe$RF_manual_label), p = 0.75)

train_spe <- lab_spe[,trainIndex$Resample1]
test_spe <- lab_spe[,-trainIndex$Resample1]

# get scaled count and
# ROSE smaple for the minor cell types 
train_df <- as.data.frame(t(assay(train_spe, "scaled"))) %>% mutate(RF_manual_label = factor(train_spe$RF_manual_label))
# find the most major cell type (= "max_xelltype"). All the other cell types will be minor cell types.
max_celltype <- table(train_spe$RF_manual_label) %>% which.max() %>% names()
# repeat ROSE sample for all minor cell types with "max_celltype"
rose_df <- 
  lapply(celltypes[celltypes !=max_celltype], function(ct){
    subdf <- train_df[train_df$RF_manual_label %in% c(max_celltype, ct),]
    col_ori <- colnames(subdf)
    colnames(subdf) <- col_ori %>% gsub("-","_",.) # remove "-" as it causes error in ROSE
    rose_subdf <- ROSE(formula = RF_manual_label ~ ., data  = subdf)$data     
    colnames(rose_subdf) <- col_ori # put back after ROSE
    rose_subdf
  }) %>% do.call("rbind",.)
# down sample "max_celltype" to the mean number of cells for all the other cell classes
n <- table(rose_df$RF_manual_label)[names(table(rose_df$RF_manual_label)) != max_celltype] %>% mean() %>% as.integer()
# combine all the minor cell types with ROSE sampling and down sampled "max_celltype"
rose_df <-rbind(rose_df[sample(which(rose_df$RF_manual_label == max_celltype), n),] , rose_df[rose_df$RF_manual_label != max_celltype,])

# get matrix for training
cur_mat <- as.matrix(rose_df[,-ncol(rose_df)]) 

# Define fit parameters for 5-fold cross validation
fitControl <- trainControl(method = "cv",
                           number = 5)
# Train a random forest classifier
set.seed(4)
rffit_gt <- train(x = cur_mat, 
                  y = rose_df$RF_manual_label,
                  method = "rf", 
                  ntree = 1000,
                  tuneLength = 5,
                  trControl = fitControl)
rffit_gt

# Predict the cell phenotype labels of the test data
cur_pred <- predict(rffit_gt, newdata = t(assay(test_spe, "scaled")))
cm <- confusionMatrix(data = cur_pred, 
                      reference = factor(test_spe$RF_manual_label), 
                      mode = "everything")
print(cm)


stopCluster(cl)
```



### Repeat training Random forest classfier using decompressed data
```{r}
sce <- SCE$decompressed
```

#### make labels for training based on threshold of scaled expression
```{r}
label_df <- 
  data.frame(Neut = as.numeric(assay(sce["MPO",],"scaled") > 0.3), 
             Fibro = as.numeric(assay(sce["SMA",],"scaled") > 0.7), 
             Endo = as.numeric(assay(sce["CD31",],"scaled") > 0.5), 
             Plasma = as.numeric(assay(sce["CD38",],"scaled") > 0.5), 
             NK = as.numeric(assay(sce["CD7",],"scaled") > 0.6 & 
                             assay(sce["CD3",],"scaled") < 0.2 & 
                             assay(sce["CD4",],"scaled") < 0.2 & 
                             assay(sce["CD8a",],"scaled") < 0.2), 
             migDC = as.numeric(assay(sce["DC-LAMP",],"scaled") > 0.5), 
             pDC = as.numeric(assay(sce["CD303",],"scaled") > 0.7), 
             Macro1 = as.numeric(assay(sce["CD68",],"scaled") > 0.6 ),
             Macro2 = as.numeric(assay(sce["CD163",],"scaled") > 0.5), 
             B = as.numeric(assay(sce["CD20",],"scaled") > 0.4),
             Tc = as.numeric(assay(sce["CD8a",],"scaled") > 0.4 & 
                             assay(sce["CD4",],"scaled") < 0.4), 
             Treg = as.numeric(assay(sce["FOXP3",],"scaled") > 0.6 & 
                               assay(sce["CD3",],"scaled") > 0.1), 
             Th = as.numeric(assay(sce["CD4",],"scaled") > 0.5 & 
                             assay(sce["CD3",],"scaled") > 0.1 & 
                             assay(sce["FOXP3",],"scaled") < 0.5 & 
                             assay(sce["CD8a",],"scaled") < 0.3))
```

#### make final labels by selecting one cell type for the cells with multiple labels
```{r}
# define markers that define celltypes
celltypes <- c("Neut","Fibro","Endo" ,"Plasma","NK","migDC","pDC","Macro1","Macro2","B","Tc","Treg","Th")
markers <- c("MPO","SMA","CD31","CD38","CD7","DC-LAMP","CD303","CD68","CD163","CD20","CD4","FOXP3","CD8a")

# get celltype based on max marker expression (only used when multiple labels were assigned to a cell)
label_mat <- label_df %>% as.matrix() %>% t() # convert to matrix
max_celltype <- 
  (assay(sce[markers,],"scaled") * label_mat) %>% apply(2, which.max) %>% celltypes[.] 

# get final labeled cells by selecting "max_celltype" when multiple labels were assigned
RF_manual_label <- 
  ifelse(rowSums(label_df) > 1, max_celltype, 
    ifelse(rowSums(label_df) == 1, colnames(label_df)[apply(label_df, 1, which.max)],"unlabeled")) 

sce$RF_manual_label <- RF_manual_label
# RF_manual_label %>% table()
```

#### train RF with ROSE sampling for balancing the dataset
```{r}
# for parallel processing
cl <- makePSOCKcluster(ncore)
registerDoParallel(cl)

# Split between labeled and unlabeled cells
lab_spe <- sce[,sce$RF_manual_label != "unlabeled"]
unlab_spe <- sce[,sce$RF_manual_label == "unlabeled"]


# Randomly split into train and test data
set.seed(4)
trainIndex <- createDataPartition(factor(lab_spe$RF_manual_label), p = 0.75)

train_spe <- lab_spe[,trainIndex$Resample1]
test_spe <- lab_spe[,-trainIndex$Resample1]

# get scaled count and
# ROSE smaple for the minor cell types 
train_df <- as.data.frame(t(assay(train_spe, "scaled"))) %>% mutate(RF_manual_label = factor(train_spe$RF_manual_label))
# find the most major cell type (= "max_xelltype"). All the other cell types will be minor cell types.
max_celltype <- table(train_spe$RF_manual_label) %>% which.max() %>% names()
# repeat ROSE sample for all minor cell types with "max_celltype"
rose_df <- 
  lapply(celltypes[celltypes !=max_celltype], function(ct){
    subdf <- train_df[train_df$RF_manual_label %in% c(max_celltype, ct),]
    col_ori <- colnames(subdf)
    colnames(subdf) <- col_ori %>% gsub("-","_",.) # remove "-" as it causes error in ROSE
    rose_subdf <- ROSE(formula = RF_manual_label ~ ., data  = subdf)$data     
    colnames(rose_subdf) <- col_ori # put back after ROSE
    rose_subdf
  }) %>% do.call("rbind",.)
# down sample "max_celltype" to the mean number of cells for all the other cell classes
n <- table(rose_df$RF_manual_label)[names(table(rose_df$RF_manual_label)) != max_celltype] %>% mean() %>% as.integer()
# combine all the minor cell types with ROSE sampling and down sampled "max_celltype"
rose_df <-rbind(rose_df[sample(which(rose_df$RF_manual_label == max_celltype), n),] , rose_df[rose_df$RF_manual_label != max_celltype,])

# get matrix for training
cur_mat <- as.matrix(rose_df[,-ncol(rose_df)]) 

# Define fit parameters for 5-fold cross validation
fitControl <- trainControl(method = "cv",
                           number = 5)
# Train a random forest classifier
set.seed(4)
rffit_dc <- train(x = cur_mat, 
                  y = rose_df$RF_manual_label,
                  method = "rf", 
                  ntree = 1000,
                  tuneLength = 5,
                  trControl = fitControl)
rffit_dc

# Predict the cell phenotype labels of the test data
cur_pred <- predict(rffit_dc, newdata = t(assay(test_spe, "scaled")))
cm <- confusionMatrix(data = cur_pred, 
                      reference = factor(test_spe$RF_manual_label), 
                      mode = "everything")
print(cm)


stopCluster(cl)
```

### save trained RF classifier
```{r}
# save rffit 
out.path <- file.path(project.path, "RF")
if (!dir.exists(out.path)) {dir.create(out.path, recursive=TRUE)}
saveRDS(rffit_gt, file.path(out.path,"rffit_gt.rds"))
saveRDS(rffit_dc, file.path(out.path,"rffit_dc.rds"))

```

### predict cell types using trained RF classifier
```{r}
set.seed(2404)
# cell types according to the max probability predicted by RF
cell_class_gt <- as.character(predict(rffit_gt, newdata = t(assay(SCE$ground_truth, "scaled")), type = "raw"))
cell_class_dc <- as.character(predict(rffit_dc, newdata = t(assay(SCE$decompressed, "scaled")), type = "raw"))
# predicted cell type probability for each cell
cell_prob_gt <- predict(rffit_gt, newdata = t(assay(SCE$ground_truth, "scaled")), type = "prob")
cell_prob_dc <- predict(rffit_dc, newdata = t(assay(SCE$decompressed, "scaled")), type = "prob")
```

### recall/precision/f1
```{r, results="asis",fig.height = 4, fig.width = 8, fig.align = "center"}
# filter undefined cells (maximum probability lower than 0.8)  
defined_cells <- rowMax(as.matrix(cell_prob_gt)) > 0.8
celltype_ann_gt <- cell_class_gt[defined_cells]
celltype_ann_dc <- cell_class_dc[defined_cells]
# calculate normalized confusion matrix (mat1: row_wise, mat2: col_wise)
mat1 <- table(celltype_ann_gt, celltype_ann_dc) %>% prop.table(margin = 1)
mat2 <- table(celltype_ann_gt, celltype_ann_dc) %>% prop.table(margin = 2)

h1 <- Heatmap(mat1, name = "Proportion\neach_row",  
        column_title = "Decompressed", row_title = "Ground_truth",
        cluster_columns = F, cluster_rows = F, border_gp = gpar(col = "black", lty = 1),
        width = ncol(mat1)*unit(5, "mm"), height = nrow(mat1)*unit(5, "mm"),
        col = colorRamp2(c(0, 1), c("white", "navy")),rect_gp = gpar(col = "gray", lwd = 1))  
h2 <- Heatmap(mat2, name = "Proportion\neach_col",  
        column_title = "Decompressed", row_title = "Ground_truth",
        cluster_columns = F, cluster_rows = F, border_gp = gpar(col = "black", lty = 1),
        width = ncol(mat2)*unit(5, "mm"), height = nrow(mat2)*unit(5, "mm"),
        col = colorRamp2(c(0, 1), c("white", "firebrick4")),rect_gp = gpar(col = "gray", lwd = 1))  
draw(h1+h2)
```


```{r, results="asis",fig.height = 3, fig.width = 5, fig.align = "center"}
recall <- diag(mat1) 
precision <- diag(mat2)
f1 <- 2*recall*precision/(recall + precision)
df <- data.frame(Recall = recall, Precision = precision, F1 = f1, Cell_types = names(f1), 
                 ncell_gt = as.vector(table(celltype_ann_gt)), ncell_dc = as.vector(table(celltype_ann_dc)))
p <- 
  ggplot(df, aes(x= Cell_types, y = F1))+  
  geom_col(width = 0.7, position = position_dodge2(), fill = "grey35") + theme_bw() + scale_y_continuous(expand = c(0,0), limits = c(0,1)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),panel.border = element_blank(), axis.line = element_line())  
print(p)
```
```{r}
cat("mean F1/recall/precision/ncells: ", mean(f1),"/", mean(recall), "/", mean(precision),"/", table(defined_cells)["TRUE"],"\n" )
```


### mean AUROC for all cell types 
```{r, results="asis",fig.height = 3, fig.width = 5, fig.align = "center"}
# filter undefined cells (maximum probability lower than 0.8)  
defined_cells <- rowMax(as.matrix(cell_prob_gt)) > 0.8
# calculate AUROC for all cell types. Each ROC is calculated for one vs others.
df <-
  sapply(celltypes,function(cur_type){
    auc <- auc(ifelse(cell_class_gt[defined_cells] == cur_type, cur_type, "others"),
               cell_prob_dc[defined_cells,cur_type])
    auc
    }) %>% data.frame(AUROC = .) %>% mutate(Cell_types = rownames(.)) 

ggplot(df, aes(x = Cell_types, y = AUROC)) +
  geom_col(width = 0.7 , fill = "grey35") + theme_bw() +
  scale_y_continuous(expand = c(0,0)) + coord_cartesian(ylim = c(0.5,1)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),panel.border = element_blank(), axis.line = element_line()) 
```
```{r}
cat("Mean AUROC is:", mean(df$AUROC))
```

### Visualize marker expression for each cell type defined by RF from ground_truth or decompressed data
```{r}
SCE$ground_truth$RF <- ifelse(defined_cells, cell_class_gt, "undefined")
SCE$decompressed$RF <- ifelse(defined_cells, cell_class_dc, "undefined")
```

```{r, results="asis",fig.height = 4.5, fig.width =8, fig.align = "center"}

# take median marker expression for each cell types
# RF based on GT data
if (!"undefined" %in% celltypes) celltypes <- c(celltypes,"undefined")

h1 <- 
  as.data.frame(t(assay(SCE$ground_truth,"scaled"))) %>% 
  mutate(RF = SCE$ground_truth$RF) %>% 
  group_by(RF)  %>% 
  summarise(across(everything(), median)) %>%
  column_to_rownames("RF") %>% 
  Heatmap(col = c("white","firebrick4"), rect_gp = gpar(col = "grey", lwd = 1), border_gp = gpar(col = "black", lty = 1), 
          column_order = rownames(SCE$ground_truth), column_title = "Ground truth expression", row_order = celltypes,
          width = ncol(.)*unit(5, "mm"), height = nrow(.)*unit(5, "mm"),
          heatmap_legend_param = list(title = "Scaled_GT"))

h2 <- 
  as.data.frame(t(assay(SCE$decompressed,"scaled"))) %>% 
  mutate(RF = SCE$ground_truth$RF) %>% 
  group_by(RF)  %>% 
  summarise(across(everything(), median)) %>%
  column_to_rownames("RF") %>% 
  Heatmap(col = c("white","navy"), rect_gp = gpar(col = "grey", lwd = 1), border_gp = gpar(col = "black", lty = 1), 
          column_order = rownames(SCE$ground_truth), column_title = "Decompressed expression", row_order = celltypes,
          width = ncol(.)*unit(5, "mm"), height = nrow(.)*unit(5, "mm"),
          heatmap_legend_param = list(title = "Scaled_DC"))

draw(h1 + h2 ,column_title = "RFclusters_Groundtruth")

# draw(h1 + h2 +rowAnnotation(ncells = row_anno_barplot(as.vector(table(SCE$gt$RF))))  ,column_title = "RFclusters_Groundtruth")

# take median marker expression for each cell types
# RF based on Dc data this time
h1 <- 
  as.data.frame(t(assay(SCE$ground_truth,"scaled"))) %>% 
  mutate(RF = SCE$decompressed$RF) %>% 
  group_by(RF)  %>% 
  summarise(across(everything(), median)) %>%
  column_to_rownames("RF") %>% 
  Heatmap(col = c("white","firebrick4"), rect_gp = gpar(col = "grey", lwd = 1), border_gp = gpar(col = "black", lty = 1), 
          column_order = rownames(SCE$ground_truth), column_title = "Ground truth expression", row_order = celltypes,
          width = ncol(.)*unit(5, "mm"), height = nrow(.)*unit(5, "mm"),
           heatmap_legend_param = list(title = "Scaled_GT"))

h2 <- 
  as.data.frame(t(assay(SCE$decompressed,"scaled"))) %>% 
  mutate(RF = SCE$decompressed$RF) %>% 
  group_by(RF)  %>% 
  summarise(across(everything(), median)) %>%
  column_to_rownames("RF") %>% 
  Heatmap(col = c("white","navy"), rect_gp = gpar(col = "grey", lwd = 1), border_gp = gpar(col = "black", lty = 1), 
          column_order = rownames(SCE$ground_truth), column_title = "Decompressed expression",row_order = celltypes,
          width = ncol(.)*unit(5, "mm"), height = nrow(.)*unit(5, "mm"),
          heatmap_legend_param = list(title = "Scaled_DC"))

draw(h1 + h2, column_title = "RFclusters_Decompressed")

```














